---
title: "Post COVID-19 vaccination menstrual disturbances in the UK"
output:
  html_document:
    keep_md: true
    css: styles.css
    toc: true
    toc_float: true
    number_sections: true
---



This script allows to reproduce the analysis of reports of menstrual disturbances following post-COVID-19 vaccination.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE,message = FALSE )
```



# 1. Data preparation
## Load packages
```{r packages}

# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")
# Packages available from CRAN
##############################
library(pacman)


## Load
pacman::p_load(
     dplyr,
     gtsummary,
     rio,         # import/export
     here,        # file locator
     purrr,       # iteration
     tidyverse,
     flextable,
     ggplot2,
     forcats,
     kableExtra,
     flextable,
     Hmisc,
     pbapply,
     mice,
     GGally,
     effects,
     gridExtra,
     grid,
     lattice,
     summarytools,  # descriptive
     gtsummary, # tables
     prLogistic  # https://www.scielo.br/j/aabc/a/4h3grwPFHKYvb8fCmnhS9cb/?format=pdf&lang=en
)


```

## Load data
```{r dataload}
# list of 5 imputed datasets
multfin<-import(here("data","Imputed_list_obj1_OSF.Rda")) # imputed list

# original data used for imputation
dataor<-import(here("data","Complete_cases_obj1_OSF.Rda")) # original dataset of vaccinated people

# describe the data
# view(dfSummary(dataor) # 
```



# 2. Descriptive Table
```{r tabledesc, results='asis'}
# create tbl objects
theme_gtsummary_journal(journal = "jama")
theme_gtsummary_compact()
tbl<- 
  tbl_summary(
  select(dataor , age, bmi_group,contra_current_groupall, covid_group,covid_tested, vaccinated, vaccine_type,vaccine_timing),
 label = list(age ~ "Age",
            bmi_group~ "Body Mass Index",
            contra_current_groupall~ "Contraceptive use at the time of the survey", 
            covid_group~ "COVID status (type)",
            covid_tested~ "COVID status (diagnosis)", 
            vaccinated~ "Number of vaccination shots", 
            vaccine_type~ "Vaccine type",
            vaccine_timing~ "Timing of 1st dose"
    
                 )) 


# beautify
tblbest<-tbl %>%
  modify_caption("Table 1. Summary of the sample characteristics") %>%
  bold_labels()
tblbest
# convert gtsummary object into flextable to export to word
#tblbest%>%
#  as_flex_table()%>%
#  flextable::save_as_docx(path = "Table1.docx") 


```

# 3. Logistic regression
## Univariable analyses
### Models and output table 
```{r logistic_univariate, results='asis'}
# set global R options
pboptions(type = "timer", char = "=") # initialize progress bar

# set list of exposures to test
exposures <- c(
    Cs(
        age,
        ethnic_group,
        med_lastyr_binary_num,
        vit_lastyr_binary_num,
        maritalstatus,
        gender,
        bmi_group,
        physact_before,
        income_before,
        smoke_before,
        contra_current_groupall,
        cyclelength_before_group,
        period_lengh_before_group,
        heavyperiod_before,
        cycle_irreg_before,
        nbdeliveries,
        vaccine_type,
        vaccine_timing,
        covid_group,
        covid_tested,
        vaccinated,
        changesmenses_num,
        lifesatchanges,
        disease_before_endometriosis_num,
        disease_before_pcos_num,
        disease_before_underthyroid_num,
        disease_before_overthyroid_num,
        disease_before_uterpolyp_num,
        disease_before_uterfibroid_num,
        disease_before_intercystitis_num,
        disease_before_eatingdisord_num,
        liveuk,
        edu_group
   
    )
)




### Univariable ------------------------------------------------------------



## model function
models <- function(x) {
    lapply(multfin, function(y)
        glm(as.formula(
            paste0(
                "vaccine_changescycle_binary ~  ",
                x
                
            )
        ), data = y, model=TRUE, family=binomial(link = "log"))
    )
}

## run logistic models
models_univariate <- as.list(seq(1,length(exposures))) # create list to store model results
library(pbapply)
models_univariate <- pblapply(exposures, models)



### Pool -------------------------------------------------------------------

pool_univariate <- as.list(seq(1,length(exposures))) # create list to store pool results

# run pool
for(j in seq_along(exposures)) {
    pool_univariate[[j]] <- pool(models_univariate[[j]])
}



### p values under FDR---------------------------------------------------------------

library(data.table)
smry <-lapply(pool_univariate,
             summary,
              conf.int = TRUE,
              conf.level = 0.99)
all_models <- rbindlist(smry)



# this is the FDR p values
all_models$q.value <- p.adjust(all_models$p.value,method = "BH")



## Table with adjusted p values--------------------------------------------------

all_models2<-all_models%>% filter (term!="(Intercept)")# to remove the intercept from the output
row<- which(all_models2$q.value<0.05) # to highlight in red those which are significant
library(kableExtra)

# change names
names(all_models2)<-c("term","estimate","std.error","statistic","df","p.value","lowCI","highCI","q.value")

# create the table
table<-all_models2%>% filter (term!="(Intercept)")%>%
  mutate(PR=exp(estimate))%>% 
  mutate(PRConf.low=exp(lowCI))%>% 
  mutate(PRConf.high=exp(highCI))%>% 
  select(term,PR,PRConf.low,PRConf.high,statistic,df,p.value, q.value) %>%
  kbl(caption = "Univariable models adjusted p-values") %>%
  kable_paper(bootstrap_options = "striped", full_width = F)%>%
  row_spec(row=c(row), bold = T, color = "white", background = "#D7261E")%>%
  pack_rows("Age", 1,1) %>%
  pack_rows("Ethnic Group", 2,2) %>%
    pack_rows("Medication Use", 3,3) %>%
      pack_rows("Vitamins Use", 4,4) %>%
  pack_rows("Marital status", 5, 6) %>%
  pack_rows("Gender", 7,7) %>%
  pack_rows("BMI", 8, 10) %>%
   pack_rows("Physical activity", 11, 14) %>%
  pack_rows("Income", 15, 19) %>%
    pack_rows("Smoking", 20, 21) %>%
    pack_rows("Contraception", 22, 26) %>%
    pack_rows("Cycle length", 27, 29) %>%
     pack_rows("Period length", 30, 35) %>%
  pack_rows("Heavy Bleeding", 36,36) %>%
  pack_rows("Irregular cycles", 37, 39) %>%
   pack_rows("Nb deliveries", 40, 42) %>%
     pack_rows("Vaccine type", 43,43) %>%
   pack_rows("Vaccine timing", 44, 46) %>%
    pack_rows("COVID group", 47,48) %>%
      pack_rows("COVID tested", 49, 50) %>%
        pack_rows("Nb shots", 51, 51) %>%
    pack_rows("Changes in menstrual cycles over the last year", 52,52) %>%
      pack_rows("Life satisfaction changes", 53, 53) %>%
   pack_rows("Endometriosis", 54, 54) %>%
   pack_rows("PCOS", 55, 55) %>%
   pack_rows("Underactive Thyroid", 56, 56) %>%
   pack_rows("Overactive Thyroid", 57, 57) %>%
   pack_rows("Uterine Polyps", 58, 58) %>%
   pack_rows("Uterine Fibroids", 59, 59) %>%
   pack_rows("Inter cystitis", 60, 60) %>%
   pack_rows("Eating disorders", 61, 61) %>%
  pack_rows("Country of residence", 62, 64) %>%
  pack_rows("Education",65,67)%>%
  kable_styling(full_width = T)

# save
#library(kableExtra)

table

#table%>%
#   save_kable("TableSI_univariable.html")

# print

#library(reporter)
#library(kableExtra)
#tbl <- create_table(all_models2) %>% 
#  titles("Univariable models adjusted p-values")
#rpt <- create_report("TableSI_univariable.pdf", font_size=  8, output_type = "PDF") %>% 
#  add_content(tbl)
#write_report(rpt)
  
```


### Plot PR and 99%CI univariable
```{r plotuniv, fig.show='asis',fig.width = 10, fig.height= 15}

#p_load("remotes")
#remotes::install_github("brooke-watson/bplots")
#p_load("bplots")

#all_models2$term
x <- data.frame(
    symptoms=c(rep("Age", 1), 
             rep("Ethnicity: Other", 1),
             rep("Medication Use: Yes", 1),
             rep("Vitamins Use: Yes", 1),
             rep("Marital status: Widowed/Separated", 1),
             rep("Marital status: Never-married/Partnered ", 1),
             rep("Gender: Other", 1) ,
             rep("BMI: Obese", 1) ,
             rep("BMI: Overweight", 1) ,
             rep("BMI: Underweight", 1) ,
             rep("Physical activity pre-pand: 60-90 minutes", 1) ,
             rep("Physical activity pre-pand: 90-120 minutes", 1) ,
             rep("Physical activity pre-pand: <30 minutes", 1) ,
             rep("Physical activity pre-pand: >120 minutes", 1) ,
             rep("Income: £13,682 to £22,140 ", 1) ,
             rep("Income: £22,140 to £29,254 ", 1) ,
             rep("Income: £39,397 to £76,144", 1) ,
             rep("Income: <£13,682", 1) ,
             rep("Income: >£76,144", 1) ,
             rep("Smoking: Past smoker", 1) ,
             rep("Smoking: Current smoker**", 1) ,
             rep("Contraception: Combined***", 1) ,
             rep("Contraception: Copper IUD", 1) ,
             rep("Contraception: Other", 1) ,
             rep("Contraception: Progestogen", 1) ,
             rep("Contraception: Sterilization", 1) ,
             rep("Cycle length pre-pand: Short cycles", 1) ,
             rep("Cycle length pre-pand: Long cycles", 1) ,
             rep("Cycle length pre-pand: Irregular", 1) ,
             rep("Period length pre-pand: <4 days", 1),
             rep("Period length pre-pand: 4 days", 1),
             rep("Period length pre-pand: 6 days", 1),
             rep("Period length pre-pand: 7 days", 1),
             rep("Period length pre-pand: >7 days", 1),
             rep("Period length pre-pand: Irregular", 1),
             rep("Heavy Bleeding pre-pand", 1),
             rep("Irregular cycles pre-pand: 2-5 days", 1) ,
             rep("Irregular cycles pre-pand: >5 days", 1) ,
             rep("Irregular cycles pre-pand: No periods", 1) ,
             rep("Nb deliveries :1", 1),
             rep("Nb deliveries: 2", 1),
             rep("Nb deliveries: 3+", 1),
             rep("Vaccine type: Pfizer-BioNTech",1),
             rep("Vaccine timing: Feb 21", 1) ,
             rep("Vaccine timing: Jan 21", 1) ,
             rep("Vaccine timing: March 21", 1) ,
             rep("COVID type: Long COVID ***", 1) ,
             rep("COVID type: Acute COVID ***", 1) ,
             rep("COVID diagnosis: Self-diagnosed +***", 1) ,
             rep("COVID diagnosis: Tested  +**", 1) ,
             rep("Nb vaccine shots: 2 ",  1) ,
             rep("Changes in menstrual cycles over the last year***", 1),
             rep("Life satisfaction changes", 1) ,
             rep("Endometriosis", 1),
             rep("PCOS", 1),
             rep("Underactive Thyroid", 1),
             rep("Overactive Thyroid", 1) ,
             rep("Uterine Polyps", 1),
             rep("Uterine Fibroids", 1),
             rep("Interstitial cystitis", 1) ,
             rep("Eating disorders", 1),
             rep("Country of residence: Northern Ireland", 1) ,
             rep("Country of residence: Scotland", 1) ,
             rep("Country of residence: Wales", 1) ,
             rep("Education: Secondary/Higher",1),
              rep("Education: Primary/Secondary",1),
              rep("Education: University",1)) ,
    PR=c(exp(all_models2$estimate)),
    Lower=c(exp(all_models2$lowCI)),
    Upper=c(exp(all_models2$highCI)),
    Variables=c(rep("Age", 1), 
             rep("Ethnicity", 1),
            rep("Medication Use", 1),
            rep("Vitamins Use", 1),
            rep("Marital status", 2),
  rep("Gender", 1) ,
  rep("BMI", 3) ,
   rep("Physical activity pre-pand", 4) ,
  rep("Income", 5) ,
    rep("Smoking", 2) ,
    rep("Contraception", 5) ,
    rep("Cycle length pre-pand", 3) ,
     rep("Period length pre-pand", 6),
  rep("Heavy Bleeding pre-pand", 1),
  rep("Irregular cycles pre-pand", 3) ,
   rep("Nb deliveries", 3),
     rep("Vaccine type",1),
   rep("Vaccine timing", 3) ,
    rep("COVID type", 2) ,
      rep("COVID diagnosis", 2) ,
        rep("Nb vaccine shots",  1) ,
    rep("Changes in menstrual cycles over the last year", 1),
      rep("Life satisfaction changes", 1) ,
   rep("Endometriosis", 1),
   rep("PCOS", 1),
   rep("Underactive Thyroid", 1),
   rep("Overactive Thyroid", 1) ,
   rep("Uterine Polyps", 1),
   rep("Uterine Fibroids", 1),
   rep("Interstitial cystitis", 1) ,
   rep("Eating disorders", 1),
  rep("Country of residence", 3) ,
  rep("Education",3))
)           
                        
                        


# Set colours
library(RColorBrewer)
# Define the number of colors you want
p_load(randomcoloR)
set.seed(782)
nb.cols <- 33
mycolors <- c(distinctColorPalette(k = nb.cols, altCol = FALSE, runTsne = FALSE))




x<-x%>%
  mutate(group=case_when(
                           
                  Variables=="Age" ~1,
                  Variables=="Ethnicity" ~2,
                  Variables=="Medication Use" ~3,
                  Variables=="Vitamins Use" ~4,
                  Variables=="Marital status" ~5,
                  Variables=="Gender" ~6,
                  Variables=="BMI" ~7,
                  Variables=="Physical activity pre-pand" ~8,
                  Variables=="Income" ~9,
                  Variables=="Smoking" ~10,
                  Variables=="Contraception" ~11,
                  Variables=="Cycle length pre-pand" ~12,
                  Variables=="Period length pre-pand" ~13,
                  Variables=="Heavy Bleeding pre-pand" ~14,
                  Variables=="Irregular cycles pre-pand" ~15,
                  Variables=="Nb deliveries" ~16,
                  Variables=="Vaccine type" ~17,
                  Variables=="Vaccine timing" ~18,
                  Variables=="COVID type" ~19,
                  Variables=="COVID diagnosis" ~20,
                  Variables=="Nb vaccine shots" ~21,
                  Variables=="Changes in menstrual cycles over the last year" ~22,
                  Variables=="Life satisfaction changes" ~23,
                  Variables=="Endometriosis" ~24,
                  Variables=="PCOS" ~25,
                      Variables=="Underactive Thyroid" ~26,
                      Variables=="Overactive Thyroid" ~27,
                      Variables=="Uterine Polyps" ~28,
                      Variables=="Uterine Fibroids" ~29,
                      Variables=="Interstitial cystitis" ~30,
                      Variables=="Eating disorders" ~31,
                      Variables=="Country of residence" ~32,
                      Variables=="Education" ~33
                           
                           ))

x$group<-as.factor(x$group)
x$Variables<-as.factor(x$Variables)

# must use font Avenir for iScience
# First download the .ttf file into windows/mac
##
#install.packages("devtools")
#require(devtools)
#install_github("Rttf2pt1", "wch")
#library(extrafont)
#extrafont::font_import()

#font_import(paths = "C:/Users/Dell/AppData/Local/Microsoft/Windows/Fonts")

# Plot
plot<-x %>% 
  ggplot(aes(x = PR, y=Variables)) + 
  labs(y = "")+
# geom_rect(aes(xmin = 0, 
#               xmax = 5,
#               ymin = -Inf, 
#               ymax = Inf),
#fill = "white")+
  geom_errorbarh(aes(xmin = Lower, xmax = Upper)) +
  geom_point(aes(colour = Variables, shape = Variables), size = 5 ) +
  geom_vline(aes(xintercept = 1), linetype = 2, col="red") +
  scale_shape_manual(values = rep(15, 67)) +
 # scale_fill_manual(values = mycolors) +
  scale_color_manual(values= mycolors)+

  scale_x_log10() +
  coord_cartesian(xlim = c(0.1, 4)) +
  facet_grid(symptoms~., switch = "y",scales = "free_y") +
 # theme_avenir()+
  theme_bw() +
 # theme(legend.position = "none")+
  theme(panel.spacing.y = unit(2, "points"),
        panel.border = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.length.y = unit(1, "points"),
        strip.text.y.left = element_text(angle = 0),
        strip.background.y = element_blank(),
        strip.placement = "outside",
        axis.line = element_line()
      
        )+ theme(text = element_text(size = 12))    


     
# control the legend
plot+guides(shape=FALSE, size=FALSE, fill=FALSE,colour=guide_legend(ncol=1))

# save the plot
ggsave(filename="Figure2.jpeg", width = 30,  height = 40, units = "cm",dpi = 300)

# save the plot
ggsave(filename="Figure2.pdf", width = 30,  height = 30, units = "cm",dpi = 300)
```

We found that smoking behaviour (current smoker), contraceptive type, COVID-19 history and cycle changes over the last year are associated with the odds of reporting menstrual cycles changes.


## Multivariable analyses
#### Models and output tables
We take each exposure significant in the univariable models at q.value (e.g., FDR adjusted p.value) < 0.05 (Smoking, COVID history and menstrual cycle changes over the last year). Based on DAGS, only COVID status and menstrual cycle changes should be adjusted for confounders.


#### COVID status as exposure

True confounders are smoking and type of contraception

```{r logistic_covid1, results='asis'}

# set global R options
pboptions(type = "timer", char = "=") # initialize progress bar

### Exposures -------------------------------------------------------------------

# set list of exposures to test
exposures <- c(
    Cs(
     covid_group,
     covid_tested

    )
)


 #model function - multivariate

models <- function(x) {
    lapply(multfin, function(y)
        glm(as.formula(
            paste0(
                "vaccine_changescycle_binary ~ smoke_before+contra_current_groupall+",
                x
                
            )
        ), data = y, model = TRUE,family=binomial(link = "log"))
    )
}


## run  models
models_test <- as.list(seq(1,length(exposures))) # create list to store model results
models_test <- pblapply(exposures, models)



### Pool -------------------------------------------------------------------
pool_tests <- as.list(seq(1,length(exposures))) # create list to store pool results


# run pool
for(j in seq_along(exposures)) {
    pool_tests[[j]] <- pool(models_test[[j]])
}



### p values under FDR-------------------------------------------------------------------

library(data.table)
smry1 <-lapply(pool_univariate,
             summary,
              conf.int = TRUE,
            conf.level = 0.95)
smry2 <-lapply(pool_tests,
             summary,
              conf.int = TRUE,
            conf.level = 0.95)

all_models <- rbindlist(c(smry1,smry2))





# this is the FDR p values
all_models$q.value <- p.adjust(all_models$p.value,method = "BH")



## Table with adjusted p values - covid tested  -------------------------------------------------------------------

library(kableExtra)


# subsetting the last model
all_models2<-all_models%>% 
filter(row_number() >= (n() - 9)) %>%
filter (term!="(Intercept)")# to remove the intercept from the output

# have significant results in red
row<- which(all_models2$q.value<0.05) # to highlight in red those which are significant

# change names
names(all_models2)<-c("term","estimate","std.error","statistic","df","p.value","lowCI","highCI","q.value")

# create the table
# change row names

all_models2$term <- c("Past smoker","Current smoker","Combined","Copper IUD","Other","Progestin only","Sterilized","Self diagnosed +","Tested +")

# change column names
table<-all_models2%>% filter (term!="(Intercept)")%>%
  mutate(PR=exp(estimate))%>% 
  mutate(PRConf.low=exp(lowCI))%>% 
  mutate(PRConf.high=exp(highCI))%>% 
  select(term,PR,PRConf.low,PRConf.high,statistic,df,p.value, q.value) %>%
  kbl(caption = "Multivariable model adjusted p-values",
      col.names = c("Variable",
                    "PR",
                    "95CI_Lower",
                    "95CI_Higher",
                    "Statistic",
                    "Df",
                    "P value",
                    "Q value")) %>%
  kable_paper(bootstrap_options = "striped", full_width = F
              )%>%
  row_spec(row=c(row), bold = T, color = "white", background = "#D7261E")%>%
  pack_rows("Smoking", 1,2) %>%
    pack_rows("Contraception", 3,7) %>%
  pack_rows("Covid Status", 8, 9) %>%
  kable_styling(full_width = T)


table%>%
   save_kable("TableSI_multivariable_COVID_tested.html")
  
table




## Table with adjusted p values - long covid -------------------------------------------------------------------

library(kableExtra)
# subsetting the model we want
all_models3<-all_models%>% 
filter(row_number() <= 110, row_number() >= 101) %>%
filter (term!="(Intercept)")# to remove the intercept from the output

# have significant results in red
row<- which(all_models3$q.value<0.05) # to highlight in red those which are significant

# change names
names(all_models3)<-c("term","estimate","std.error","statistic","df","p.value","lowCI","highCI","q.value")

# create the table
# change row names

all_models3$term <- c("Past smoker","Current smoker","Combined","Copper IUD","Other","Progestin only","Sterilized","Long Covid","Acute Covid")

# change column names
table<-all_models3%>% filter (term!="(Intercept)")%>%
  mutate(PR=exp(estimate))%>% 
  mutate(PRConf.low=exp(lowCI))%>% 
  mutate(PRConf.high=exp(highCI))%>% 
  select(term,PR,PRConf.low,PRConf.high,statistic,df,p.value, q.value) %>%
  kbl(caption = "Multivariable model adjusted p-values",
      col.names = c("Variable",
                    "PR",
                    "95CI_Lower",
                    "95CI_Higher",
                    "Statistic",
                    "Df",
                    "P value",
                    "Q value")) %>%
  kable_paper(bootstrap_options = "striped", full_width = F
              )%>%
  row_spec(row=c(row), bold = T, color = "white", background = "#D7261E")%>%
  pack_rows("Smoking", 1,2) %>%
    pack_rows("Contraception", 3,7) %>%
  pack_rows("Covid Status", 8, 9) %>%
  kable_styling(full_width = T)


table%>%
   save_kable("TableSI_multivariable_COVID_type.html")

table
```



#### Menstrual cycle changes over the last year as exposure

```{r logistic_multivariate_ms, results='asis'}
# set global R options
pboptions(type = "timer", char = "=") # initialize progress bar

### Exposures -------------------------------------------------------------------

# set list of exposures to test
exposures <- c(
    Cs(
     covid_group,
     covid_tested

    )
)


 #model function - multivariate

models <- function(x) {
    lapply(multfin, function(y)
        glm(as.formula(
            paste0(
                "vaccine_changescycle_binary ~ smoke_before+contra_current_groupall+changesmenses_num+",
                x
                
            )
        ), data = y, model = TRUE,family=binomial(link = "log"))
    )
}


## run  models
models_test <- as.list(seq(1,length(exposures))) # create list to store model results
models_test <- pblapply(exposures, models)



### Pool -------------------------------------------------------------------
pool_tests <- as.list(seq(1,length(exposures))) # create list to store pool results


# run pool
for(j in seq_along(exposures)) {
    pool_tests[[j]] <- pool(models_test[[j]])
}



### p values under FDR-------------------------------------------------------------------

library(data.table)
smry1 <-lapply(pool_univariate,
             summary,
              conf.int = TRUE,
            conf.level = 0.95)
smry2 <-lapply(pool_tests,
             summary,
              conf.int = TRUE,
            conf.level = 0.95)

all_models <- rbindlist(c(smry1,smry2))





# this is the FDR p values
all_models$q.value <- p.adjust(all_models$p.value,method = "BH")



## Table with adjusted p values - covid tested  -------------------------------------------------------------------

library(kableExtra)


# subsetting the last model
all_models2<-all_models%>% 
filter(row_number() >= (n() - 10)) %>%
filter (term!="(Intercept)")# to remove the intercept from the output

# have significant results in red
row<- which(all_models2$q.value<0.05) # to highlight in red those which are significant

# change names
names(all_models2)<-c("term","estimate","std.error","statistic","df","p.value","lowCI","highCI","q.value")

# create the table
# change row names

all_models2$term <- c("Past smoker","Current smoker","Combined","Copper IUD","Other","Progestin only", "Sterilized","Prior changes in menstrual cycles","Self diagnosed +","Tested +")

# change column names
table<-all_models2%>% filter (term!="(Intercept)")%>%
  mutate(PR=exp(estimate))%>% 
  mutate(PRConf.low=exp(lowCI))%>% 
  mutate(PRConf.high=exp(highCI))%>% 
  select(term,PR,PRConf.low,PRConf.high,statistic,df,p.value, q.value) %>%
  kbl(caption = "Multivariable model adjusted p-values",
      col.names = c("Variable",
                    "PR",
                    "95CI_Lower",
                    "95CI_Higher",
                    "Statistic",
                    "Df",
                    "P value",
                    "Q value")) %>%
  kable_paper(bootstrap_options = "striped", full_width = F
              )%>%
  row_spec(row=c(row), bold = T, color = "white", background = "#D7261E")%>%
  pack_rows("Smoking", 1,2) %>%
    pack_rows("Contraception", 3,7) %>%
      pack_rows("Prior changes in menses", 8,8) %>%
  pack_rows("Covid Status", 9, 10) %>%
  kable_styling(full_width = T)


table%>%
   save_kable("TableSI_multivariable_menstruation.html")

table

## Table with adjusted p values - long covid -------------------------------------------------------------------

library(kableExtra)
# subsetting the model we want
all_models3<-all_models%>% 
filter(row_number() <= 111, row_number() >= 101) %>%
filter (term!="(Intercept)")# to remove the intercept from the output

# have significant results in red
row<- which(all_models3$q.value<0.05) # to highlight in red those which are significant

# change names
names(all_models3)<-c("term","estimate","std.error","statistic","df","p.value","lowCI","highCI","q.value")

# create the table
# change row names

all_models3$term <- c("Past smoker","Current smoker","Combined","Copper IUD","Other","Progestin only", "Sterilization", "Prior changes in menstrual cycles","COVID + long","COVID + short")

# change column names
table<-all_models3%>% filter (term!="(Intercept)")%>%
  mutate(PR=exp(estimate))%>% 
  mutate(PRConf.low=exp(lowCI))%>% 
  mutate(PRConf.high=exp(highCI))%>% 
  select(term,PR,PRConf.low,PRConf.high,statistic,df,p.value, q.value) %>%
  kbl(caption = "Multivariable model adjusted p-values",
      col.names = c("Variable",
                    "PR",
                    "95CI_Lower",
                    "95CI_Higher",
                    "Statistic",
                    "Df",
                    "P value",
                    "Q value")) %>%
  kable_paper(bootstrap_options = "striped", full_width = F
              )%>%
  row_spec(row=c(row), bold = T, color = "white", background = "#D7261E")%>%
  pack_rows("Smoking", 1,2) %>%
    pack_rows("Contraception", 3,7) %>%
      pack_rows("Prior changes in menses", 8,8) %>%
  pack_rows("Covid Status", 9, 10) %>%
  kable_styling(full_width = T)


table%>%
   save_kable("TableSI8_multivariable_Menstrualchanges_acute_long.html")

table
```


# 4. Plot models
#### Plot PR
```{r plot_PR, fig.show='asis',fig.height=10}
# Rename levels
levels(multfin[[1]]$covid_group)[1]<- "No Covid"
levels(multfin[[1]]$covid_group)[2]<- "Long Covid"
levels(multfin[[1]]$covid_group)[3]<- "Acute Covid"

levels(multfin[[1]]$contra_current_groupall)[5]<- "Progestin"
levels(multfin[[1]]$contra_current_groupall)[3]<- "IUD"

# Models

# Model I
modelsmoking<-glm(vaccine_changescycle_binary ~    smoke_before, data = multfin[[1]], family=binomial, model = TRUE)
#
modelchangemense<-glm(vaccine_changescycle_binary ~     smoke_before+contra_current_groupall+covid_tested+changesmenses_num, data = multfin[[1]], family=binomial, model = TRUE)
# Model II
modelchangemensegroup<-glm(vaccine_changescycle_binary ~     smoke_before+contra_current_groupall+covid_group+changesmenses_num, data = multfin[[1]], family=binomial, model = TRUE)
# Model III
modeltested<-glm(vaccine_changescycle_binary ~    smoke_before+contra_current_groupall+covid_tested, data = multfin[[1]], family=binomial, model = TRUE)
# Model IV
modelgroup<-glm(vaccine_changescycle_binary ~    smoke_before+contra_current_groupall+covid_group, data = multfin[[1]], family=binomial, model = TRUE)
# Model V
modelcontra<-glm(vaccine_changescycle_binary ~    contra_current_groupall, data = multfin[[1]], family=binomial, model = TRUE)


# List of models

models <- list( "Model I" = modelsmoking, "Model II" = modelcontra,"Model III" = modeltested, "Model IV" = modelgroup, "Model V" = modelchangemense ,"Model VI" = modelchangemensegroup)


# Plot compare models

plot_PR<-ggcoef_compare(models, 
                    type = c("faceted"),
                    conf.level = 0.99,
                    exponentiate = TRUE,
                    add_reference_rows = TRUE,
                    variable_labels = c(
                    smoke_before="Smoking behaviour",
                    contra_current_groupall= "Contraceptive use",
                    covid_tested= "COVID-19 diagnosis",
                    covid_group= "COVID-19 type",
                    changesmenses_num= "PRMC"))+ theme(text = element_text(size = 18))    


plot_PR                 # All font sizes
# Save plot

#ggsave(filename="Figure3.jpeg", width = 30,  height = 20, units = "cm", dpi=300)

#
library(sjPlot)


plot_models(
  modelsmoking, modelcontra, modeltested,modelgroup,modelchangemense,modelchangemensegroup,
  m.labels = c("Smoking", "Contraception", "COVID tested","COVID group","modelgroup","modelchangemense"),
  vline.color = "grey70",
  show.values = FALSE, show.p = TRUE, p.shape = TRUE

)+theme_classic()
```



#### Plot predicted probability

```{r proba, fig.show='asis'}
# set up
trellis.device()
trellis.par.set(list(axis.text = list(font = 1, cex=1)))
trellis.par.set(list(par.ylab.text = list(font = 1, cex=1))) 
trellis.par.set(list(par.xlab.text = list(font = 1, cex=1))) 
trellis.par.set(list(par.main.text = list(font = 1, cex=1))) 
trellis.par.set(grid.pars = list(fontfamily = "serif"))


## Plot effect of contraceptive use

a<-plot(Effect("contra_current_groupall",modelcontra), 
    lines = list(multiline = FALSE), 
     lty=0,
     lwd=6,
     level=.99,
     ylim=c(-3,-0.3),
     lattice=list(strip=list(factor.names=FALSE)),
     confint = list(style = "auto"),
     response="",
     xlab="Contraceptive type", 
     ylab= "Predicted probability",
     main="")

## Plot effect covid_tested


b<-plot(Effect("covid_tested",modeltested), 
     lines = list(multiline = T), 
     lty=0,
     lwd=6,
     level=.99,
     ylim=c(-3,-0.3),
     lattice=list(strip=list(factor.names=FALSE)),
     confint = list(style = "auto"),
     response="",
     xlab="COVID Status", 
     ylab= "Predicted probability",
     main="")

## Plot effect covid_group

c<-plot(Effect("covid_group",modelgroup), 
     lines = list(multiline = T), 
     lty=0,
     lwd=6,
     level=.99,
     ylim=c(-3,-0.3),
     lattice=list(strip=list(factor.names=FALSE)),
     confint = list(style = "auto"),
     response="",
     xlab="COVID Status", 
     ylab= "Predicted probability",
     main="")

## Plot changes menses

d<-plot(Effect("smoke_before",modelsmoking), 
     lines = list(multiline = T), 
     level=.99,
     lty=0,
     lwd=6,
     ylim=c(-3,-0.3),
     symbols=TRUE,
     lattice=list(strip=list(factor.names=FALSE)),
     confint = list(style = "auto"),
     response="",
     xlab="Smoking behaviour", 
     ylab= "Predicted probability",
     main="")


# grid arrange

plotpredictedvalues<-grid.arrange(a,b,c,d,ncol=2)
plotpredictedvalues

# save
pdf(file='Figure3.pdf', width=12,height=8) # Open PDF device with specific file name
grid.arrange(a,b,c,d,ncol=2)
dev.off() # Turn the PDF device off

grid.arrange(a,b,c,d,ncol=2)

```





# 5. Analysis on complete cases
```{r summary tables, results='asis'}

completerecords<-dataor %>% select(-c(toosoon)) %>% na.omit()
dim(completerecords)

# manipulation variables
levels(completerecords$smoke_before)[3]<-"Current Smoker"
levels(completerecords$smoke_before)[4]<-"Current Smoker"
completerecords$contra_current_groupall<-as.factor(completerecords$contra_current_groupall)
completerecords$contra_current_groupall<-relevel(completerecords$contra_current_groupall, ref = "None")


## models--------------------------------------------------------
model1<-glm(vaccine_changescycle_binary ~ smoke_before, data =completerecords, family=binomial, model = TRUE)

## model 2----------------------------------------------------

model2<-glm(vaccine_changescycle_binary ~ contra_current_groupall, data =completerecords, family=binomial, model = TRUE)

## model 3----------------------------------------------------

model3<-glm(vaccine_changescycle_binary ~   smoke_before+contra_current_groupall+covid_tested, data =completerecords, family=binomial, model = TRUE)

## model 4----------------------------------------------------

model4<-glm(vaccine_changescycle_binary ~    smoke_before+contra_current_groupall+covid_group, data =completerecords, family=binomial, model = TRUE)

## model 5----------------------------------------------------

model5<-glm(vaccine_changescycle_binary ~    smoke_before+contra_current_groupall+ changesmenses_num+covid_tested, data =completerecords, family=binomial, model = TRUE)

## model 5----------------------------------------------------

model6<-glm(vaccine_changescycle_binary ~   smoke_before+contra_current_groupall+ changesmenses_num+covid_group, data =completerecords, family=binomial, model = TRUE)


### model summary

library(modelsummary)

# plot
msuni<-modelsummary(list(model1,model2,model3,model4,model5,model6),
                    coef_rename=c(
                                 
                                  "smoke_beforeNo, but I have smoked in the past"="Past smokers",
                                  "smoke_beforeCurrent Smoker"="Current smokers",
                                  "contra_current_groupallCopper IUD"="Copper IUD",
                                  "contra_current_groupallCombined estrogen-progestin"="Combined",
                                  "contra_current_groupallProgestin only"= "Progestin only",
                                  "contra_current_groupallOther"= "Other contraceptives",
                               "contra_current_groupallSterilization"= "Sterilization",
                          
                                   
                                  "changesmenses_num"="Menstrual cycle changes over the last year",

                                  "covid_testedSelf diagnosed +"= "COVID self-diagnosed positive",
                                  "covid_testedTested  +"="COVID tested positive",
                               
                               "covid_groupCOVID + long"="Long Covid",
                                "covid_groupCOVID + short"="Acute Covid"),
                    
              
                    stars = c('*' = 0.05,'**' = 0.01,'***' = 0.001),
                    exponentiate = TRUE,estimate = "{estimate}{stars} [{conf.low}, {conf.high}]", 
                    statistic = NULL ,
                    gof_omit = ".*",title = 'Risk factors for vaccine related changes in menstrual cycles using complete cases',
                    coef_omit = "Intercept", 
                    output = "kableExtra")  

# save

save_kable(msuni, file="TableSIcompletecases.html")
msuni

```



