---
title: 'Objective 2: COVID-19 vaccination, COVID-19 disease and cycle parameters'
author: "Alex Alvergne"
date: "26/05/2021"
output:
  html_document:
    code_folding: hide
    keep_md: yes
    css: styles.css
    toc: yes
    toc_float: yes
    number_sections: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, warning=FALSE, message=FALSE, tidy=TRUE, results="asis", verbose=FALSE)
```

This analysis aims to investigate the impact of COVID-19 disease, relative to COVID-19 vaccination, on cycles.

We focus on the 4 FIGO criteria

- Frequency (normal cycle length is 24-38 days)
- Duration (normal period length is up to 8 days)
- Regularity (regular variation (shortest to longest cycle <=9 days))
- Flow volume (heavy/normal/light)
- Inter-menstrual bleeding

# Set up 

#### Packages load
```{r packages}

# Ensures the package "pacman" is installed
if (!require("pacman")) install.packages("pacman")

## Load
library(pacman)
pacman::p_load(
     rio,         # import/export
     here,        # file locator
     purrr,       # iteration
     dplyr,
     gtsummary,
     tidyverse,
     flextable,
     ggplot2,
     forcats,
     kableExtra,
     flextable,
     Hmisc,
     pbapply,
     mice,
     GGally,
     effects,
     gridExtra,
     grid,
     lattice,
     gtsummary,
     dplyr,
     DiagrammeR,
     reporter# to do the flowchart
    
)


```

#### Data load
```{r dataload}
# list
datalist<-import(here("data","Imputed_list_obj2_OSF.Rda")) # imputed list

```

# Frequency 

##### Model 
```{r frequency, echo=FALSE, include=FALSE}

# pck
p_load(nnet) # for multinomial model

# set global R options
pboptions(type = "timer", char = "=") # initialize progress bar

# set list of exposures to test
exposures <- c(
    Cs(
        covid_status_minimal  +cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num,
        
        covid_status_minimal  +cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num +lifesatchanges ,
        
         covid_status_minimal  +cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num +physicalactchanges_lastyr+eatingchanges_lastyr 
    )
)


 # model function - multivariate
 models <- function(x) {
     lapply(datalist, function(y)
         multinom(as.formula(
             paste0(
                 "cyclelength_lastyr_group ~ age_scaled + bmi_group + ",
                 x # exposure
            )
         ), data = y, model = TRUE)
     )
 }

# run  models
models_univariate <- as.list(seq(1,length(exposures))) # create list to store model results
models_univariate <- pblapply(exposures, models)





# Pool -------------------------------------------------------------------

pool_univariate <- as.list(seq(1,length(exposures))) # create list to store pool results

# run pool
for(j in seq_along(exposures)) {
    pool_univariate[[j]] <- pool(models_univariate[[j]])
}





#  create report for model with age, bmi and contraceptive use
tab<-summary(pool_univariate[[1]]) # to get results from 1st model

tab$q.value <- p.adjust(tab$p.value,method = "BH") # adjust for multiple comparisons


tab2 <- tab %>% mutate(RRR = round (exp(estimate),2),
                      LowCI = round(exp (estimate - 1.96*std.error),2),
                      HighCI = round(exp (estimate + 1.96*std.error),2),
                      p.value = round ((p.value),4),
                      q.value = round ((q.value),4))%>%
                select(y.level ,term,RRR,LowCI,HighCI, p.value, q.value)




# export
library(reporter)

tbl <- create_table(tab2) %>% 
  titles("Pooled Multivariate Models (Cycle Frequency) ")
rpt <- create_report("Multi_full_Frequency.pdf", font_size=  8, output_type = "PDF") %>% 
  add_content(tbl)
write_report(rpt)


##-------------------------------------------------------AIC models from 1st dataset
library(modelsummary)
library(kableExtra)
library(gt)
m<-multinom(cyclelength_lastyr_group ~ covid_status_minimal  +cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num+age_scaled + bmi_group , data=datalist[[1]])
m$AIC # 

m2<-multinom(cyclelength_lastyr_group ~         covid_status_minimal*cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num +age_scaled + bmi_group , data=datalist[[1]])
m2$AIC # 

m3<-multinom(cyclelength_lastyr_group ~         covid_status_minimal  *contra_past12mo_groupall+cyclelength_before_group+disease_before_binary_num + age_scaled + bmi_group, data=datalist[[1]])
m3$AIC #

m4<-multinom(cyclelength_lastyr_group ~ covid_status_minimal  *disease_before_binary_num+cyclelength_before_group + contra_past12mo_groupall+ age_scaled + bmi_group , data=datalist[[1]])
m4$AIC # 


```    

##### Print table
```{r print table_freq, results="asis"}
kable(tab2)
```

##### Plot
```{r plot_freq_normal, results="asis",  fig.width = 10}

#----------lot predicted effect sizes


mod1<-multinom(cyclelength_lastyr_group ~ covid_status_minimal + age_scaled+ bmi_group +contra_past12mo_groupall+disease_before_binary_num, data=datalist[[1]])




# Plot combined#
# Save results
library(ggeffects)
pprob_grplang <- ggeffect(mod1, terms = "covid_status_minimal")

# Build plot
plot_freq_figo1_comb<-ggplot(data = pprob_grplang,
       aes(x = x, y = predicted,
           color = response.level, group = response.level)) +
  #geom_line() +
  geom_point() +
  ggtitle("(A) Cycle frequency")+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high,
                    color = response.level,
                    group = response.level),
                width = .1) +
  scale_color_brewer(palette = "Dark2",
                     name = "",
                     labels = c("Frequent cycles",
                                "Infrequent cycles",
                                "Normal cycles")) +
  labs(
    x = "",
    y = "Probability"
  ) +
  # Set the theme
#  theme_minimal(base_family="Avenir LT Std 35 Light") +
  theme_bw()+
  theme(
    legend.position = "bottom", # move legend to the bottom
    axis.title = element_text(size = 12) # increase axis title size
  )

ggsave("plot_frequency_predicted.bmp",plot_freq_figo1_comb, width=5, height=5)

plot_freq_figo1_comb
```





# Missed or stopped
#### Model 
```{r miss , echo=FALSE, include=FALSE}

# set global R options
pboptions(type = "timer", char = "=") # initialize progress bar

# set list of exposures to test
exposures <- c(
    Cs(
  covid_status_minimal  +contra_past12mo_groupall+disease_before_binary_num,
covid_status_minimal  +cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num +lifesatchanges ,
        
         covid_status_minimal  +cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num +physicalactchanges_lastyr+eatingchanges_lastyr ,

                covid_status_minimal  +contra_past12mo_groupall+disease_before_binary_num+
+disease_before_binary_num +physicalactchanges_lastyr+eatingchanges_lastyr 
    )
)


 #model function - multivariate
models <- function(x) {
    lapply(datalist, function(y)
        glm(as.formula(
            paste0(
                "stoppedperiods_lastyr ~ age_scaled + bmi_group + ",
                x
                
            )
        ), data = y, model=TRUE, family=binomial(link="log"))
    )
}


## run  models
models_univariate <- as.list(seq(1,length(exposures))) # create list to store model results
models_univariate <- pblapply(exposures, models)







# Pool -------------------------------------------------------------------

pool_univariate <- as.list(seq(1,length(exposures))) # create list to store pool results

# run pool
for(j in seq_along(exposures)) {
    pool_univariate[[j]] <- pool(models_univariate[[j]])
}


# create report for cycle length before + contra + age + bmi + covidstatus
tab<-summary(pool_univariate[[1]])

tab$q.value <- p.adjust(tab$p.value,method = "BH")



tab2 <- tab %>% mutate(PR = round (exp(estimate),2),
                      LowCI = round(exp (estimate - 1.96*std.error),2),
                      HighCI = round(exp (estimate + 1.96*std.error),2),
                      p.value = round ((p.value),4),
                      q.value = round ((q.value),4))%>%
                select(term,PR,LowCI,HighCI, p.value, q.value)



## Report
library(reporter)

tbl <- create_table(tab2) %>% 
  titles("Pooled Multivariate Models (Periods Stopped)")
rpt <- create_report("Multi_full_Frequency_Stopped.pdf", font_size=  8, output_type = "PDF") %>% 
  add_content(tbl)
write_report(rpt)


# AIC
m<-glm(stoppedperiods_lastyr ~ covid_status_minimal  +cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num+age_scaled + bmi_group ,family=binomial(link="log"), data=datalist[[1]])
summary(m)

m2<-glm(stoppedperiods_lastyr ~         covid_status_minimal*cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num +age_scaled + bmi_group ,family=binomial(link="log"), data=datalist[[1]])
summary(m2)

m3<-glm(stoppedperiods_lastyr ~         covid_status_minimal  *contra_past12mo_groupall+cyclelength_before_group+disease_before_binary_num + age_scaled + bmi_group,  family=binomial(link="log"),data=datalist[[1]])
summary(m3)


m4<-glm(stoppedperiods_lastyr ~ covid_status_minimal  *disease_before_binary_num+cyclelength_before_group + contra_past12mo_groupall+ age_scaled + bmi_group  ,family=binomial(link="log"), data=datalist[[1]])
summary(m4)



```    

##### Print table
```{r print table_stop, results="asis"}
kable(tab2)
```
#### Plot
```{r plot_miss, results="asis", fig.width=8}

m<-glm(stoppedperiods_lastyr ~ age_scaled + bmi_group + covid_status_minimal+disease_before_binary_num+contra_past12mo_groupall  , data=datalist[[1]], family=binomial(link="log"))

# Plot combined
#
# Save results
pprob_grplang <- ggeffect(m, terms = "covid_status_minimal")

# Build plot
plot_miss_figo_covax_comb<-ggplot(data = pprob_grplang,
       aes(x = x, y = predicted)) +
 # geom_line() +
  geom_point() +
  ggtitle("(F) Periods missed")+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                width = .1) +
  scale_color_brewer(palette = "Dark2") +
  labs(
    x = "",
    y = "Probability"
  ) +
  # Set the theme
#  theme_minimal(base_family="Avenir LT Std 35 Light") +
  theme_bw()+
  theme(
    legend.position = "bottom", # move legend to the bottom
    axis.title = element_text(size = 12) # increase axis title size
  )

ggsave("plot_frequency_stop_predicted.bmp",plot_miss_figo_covax_comb, width=5, height=5)

plot_miss_figo_covax_comb
```








# Cycle Regularity 
#### Model 
```{r cyclereg , echo=FALSE, include=FALSE}

# multinomial
p_load(nnet) # for multinomial model

# set global R options
pboptions(type = "timer", char = "=") # initialize progress bar

# set list of exposures to test
exposures <- c(
    Cs(
       covid_status_minimal  +cycle_irreg_before_group+contra_past12mo_groupall+disease_before_binary_num,
        covid_status_minimal  *cycle_irreg_before_group+contra_past12mo_groupall+disease_before_binary_num

       
    )
)


 #model function - multivariate
 models <- function(x) {
     lapply(datalist, function(y)
         multinom(as.formula(
             paste0(
                 "cyclelength_irregular_lastyr_group ~ age_scaled + bmi_group + ",
                 x # exposure
            )
         ), data = y, model=TRUE)
     )
 }

## run  models
models_univariate <- as.list(seq(1,length(exposures))) # create list to store model results
models_univariate <- pblapply(exposures, models)



### Pool -------------------------------------------------------------------

pool_univariate <- as.list(seq(1,length(exposures))) # create list to store pool results

# run pool
for(j in seq_along(exposures)) {
    pool_univariate[[j]] <- pool(models_univariate[[j]])
}




# Table
tab<-summary(pool_univariate[[1]])# put in model you want to see

tab$q.value <- p.adjust(tab$p.value,method = "BH")


tab2 <- tab %>% mutate(RRR = round (exp(estimate),2),
                      LowCI = round(exp (estimate - 1.96*std.error),2),
                      HighCI = round(exp (estimate + 1.96*std.error),2),
                      p.value = round ((p.value),4),
                      q.value = round ((q.value),4))%>%
                select(y.level ,term,RRR,LowCI,HighCI, p.value, q.value)


library(reporter)

tbl <- create_table(tab2) %>% 
  titles("Pooled Multivariate Models (Cycle Regularity) ")
rpt <- create_report("Multi_full_Regularity.pdf", font_size=  8, output_type = "PDF") %>% 
  add_content(tbl)
write_report(rpt)


# check AIC
m<-multinom(cyclelength_irregular_lastyr_group ~ covid_status_minimal  +cycle_irreg_before_group+contra_past12mo_groupall+disease_before_binary_num+age_scaled + bmi_group , data=datalist[[1]])
m$AIC # 

m2<-multinom(cyclelength_irregular_lastyr_group ~ covid_status_minimal*cycle_irreg_before_group+contra_past12mo_groupall+disease_before_binary_num+ age_scaled + bmi_group , data=datalist[[1]])
m2$AIC # 

m3<-multinom(cyclelength_irregular_lastyr_group ~         covid_status_minimal  *contra_past12mo_groupall+cycle_irreg_before_group+disease_before_binary_num + age_scaled + bmi_group, data=datalist[[1]])
m3$AIC

m4<-multinom(cyclelength_irregular_lastyr_group ~ covid_status_minimal  *disease_before_binary_num+cycle_irreg_before_group + contra_past12mo_groupall+ age_scaled + bmi_group , data=datalist[[1]])
m4$AIC # 

```    


#### Plot 
```{r plot_cyclechanges, results="asis", fig.width=14}

m<-multinom(cyclelength_irregular_lastyr_group  ~  cycle_irreg_before_group+age_scaled +covid_status_minimal+ bmi_group +disease_before_binary_num  , data=datalist[[1]])

# Save results
pprob_grplang <- ggeffect(m, terms = "covid_status_minimal")

# Build plot
plot_reg_figo1_comb<-ggplot(data = pprob_grplang,
       aes(x = x, y = predicted,
           color = response.level, group = response.level)) +
  #geom_line() +
  geom_point() +
  ggtitle("(B) Cycle regularity")+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high,
                    color = response.level,
                    group = response.level),
                width = .1) +
  scale_color_brewer(palette = "Dark2",
                     name = "",
                     labels = c("Irregular [10-20days]",
                                "Irregular [20-30days]",
                                "Regular cycles")) +
  labs(
    x = "",
    y = "Probability"
  ) +
  # Set the theme
# theme_minimal(base_family="Avenir LT Std 35 Light")+
  theme_bw()+
  theme(
    legend.position = "bottom", # move legend to the bottom
    axis.title = element_text(size = 12) # increase axis title size
  )

ggsave("plot_regularity_predicted.bmp",plot_reg_figo1_comb, width=5, height=5)

plot_reg_figo1_comb

```



# Period Duration

#### Model 
```{r period_duration , echo=FALSE, include=FALSE}

# set global R options
pboptions(type = "timer", char = "=") # initialize progress bar

# set list of exposures to test
exposures <- c(
    Cs(
         covid_status_minimal  +period_lengh_before_group+contra_past12mo_groupall+disease_before_binary_num,
         covid_status_minimal  +period_lengh_before_group+contra_past12mo_groupall+disease_before_binary_num +physicalactchanges_lastyr+eatingchanges_lastyr 
   
    )
)


 #model function - multivariate
 models <- function(x) {
     lapply(datalist, function(y)
         glm(as.formula(
             paste0(
                 "period_lengh_lastyr_group ~ age_scaled + bmi_group  + ",
                 x # exposure
            )
         ), data = y, family=binomial())
     )
 }

## run  models
models_univariate <- as.list(seq(1,length(exposures))) # create list to store model results
models_univariate <- pblapply(exposures, models)







### Pool -------------------------------------------------------------------

pool_univariate <- as.list(seq(1,length(exposures))) # create list to store pool results

# run pool
for(j in seq_along(exposures)) {
    pool_univariate[[j]] <- pool(models_univariate[[j]])
}



# all models together


# Table
tab<-summary(pool_univariate[[1]])

tab$q.value <- p.adjust(tab$p.value,method = "BH")


tab2 <- tab %>% mutate(PR = round (exp(estimate),2),
                      LowCI = round(exp (estimate - 1.96*std.error),2),
                      HighCI = round(exp (estimate + 1.96*std.error),2),
                      p.value = round ((p.value),4),
                      q.value = round ((q.value),4)) %>%
                select(term,PR,LowCI,HighCI, p.value, q.value)


library(reporter)

tbl <- create_table(tab2) %>% 
  titles("Pooled Multivariate Models (Period Duration) ")
rpt <- create_report("Multi_full_Duration.pdf", font_size=  8, output_type = "PDF") %>% 
  add_content(tbl)
write_report(rpt)


# check AIC

m<-glm(period_lengh_lastyr_group ~ covid_status_minimal  +period_lengh_before_group+contra_past12mo_groupall+disease_before_binary_num+age_scaled + bmi_group ,family=binomial(), data=datalist[[1]])
summary(m)

m2<-glm(period_lengh_lastyr_group ~         covid_status_minimal*period_lengh_before_group+contra_past12mo_groupall+disease_before_binary_num +age_scaled + bmi_group ,family=binomial(), data=datalist[[1]])
summary(m2)

m3<-glm(period_lengh_lastyr_group ~         covid_status_minimal  *contra_past12mo_groupall+period_lengh_before_group+disease_before_binary_num + age_scaled + bmi_group,  family=binomial(),data=datalist[[1]])
summary(m3)


m4<-glm(period_lengh_lastyr_group ~ covid_status_minimal  *disease_before_binary_num+period_lengh_before_group + contra_past12mo_groupall+ age_scaled + bmi_group  ,family=binomial(), data=datalist[[1]])
summary(m4)


```    




##### Print table
```{r print table_reg , results="asis"}
kable(tab2)
```
#### Plot
```{r plot_p_duration, results='asis'}

m<-glm(period_lengh_lastyr_group ~ age_scaled+bmi_group  + covid_status_minimal+period_lengh_before_group +disease_before_binary_num+contra_past12mo_groupall, data=datalist[[1]], family=binomial)



# plot combined
# Save results
pprob_grplang <- ggeffect(m, terms = "covid_status_minimal")

# Build plot
plot_dur_figo_covax_comb<-ggplot(data = pprob_grplang,
       aes(x = x, y = predicted)) +
#  geom_line() +
  geom_point() +
  ggtitle("(E) Period duration (8+ days)")+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                width = .1) +
  scale_color_brewer(palette = "Dark2") +
  labs(
    x = "",
    y = "Probability"
  ) +
  # Set the theme
#  theme_minimal(base_family="Avenir LT Std 35 Light")+
  theme_bw()+
  theme(
    legend.position = "bottom", # move legend to the bottom
    axis.title = element_text(size = 12) # increase axis title size
  )

ggsave("plot_dur_predicted.bmp",plot_dur_figo_covax_comb, width=5, height=5)

plot_dur_figo_covax_comb

```


# Period Flow 

#### Model 
```{r flow , echo=FALSE, include=FALSE}
# multinomial
p_load(nnet) # for multinomial model

# set global R options
pboptions(type = "timer", char = "=") # initialize progress bar

# set list of exposures to test
exposures <- c(
    Cs(
    covid_status_minimal  +heavyperiod_before+contra_past12mo_groupall+disease_before_binary_num,
        covid_status_minimal  *heavyperiod_before+contra_past12mo_groupall+disease_before_binary_num
    )
)


# model function - multivariate
 models <- function(x) {
     lapply(datalist, function(y)
         multinom(as.formula(
             paste0(
                 "changesperiod_lastyr ~ age_scaled + bmi_group  +",
                 x # exposure
            )
         ), data = y, model = TRUE)
     )
 }

## run  models
models_univariate <- as.list(seq(1,length(exposures))) # create list to store model results
models_univariate <- pblapply(exposures, models)



### Pool -------------------------------------------------------------------

pool_univariate <- as.list(seq(1,length(exposures))) # create list to store pool results

# run pool
for(j in seq_along(exposures)) {
    pool_univariate[[j]] <- pool(models_univariate[[j]])
}




# Check AICS
m<-multinom(changesperiod_lastyr ~   covid_status_minimal  +heavyperiod_before+contra_past12mo_groupall+disease_before_binary_num+age_scaled + bmi_group , data=datalist[[1]])
m$AIC # 

m2<-multinom(changesperiod_lastyr ~ covid_status_minimal*heavyperiod_before+contra_past12mo_groupall+disease_before_binary_num+ age_scaled + bmi_group , data=datalist[[1]])
m2$AIC # 

m3<-multinom(changesperiod_lastyr ~ covid_status_minimal  *contra_past12mo_groupall+heavyperiod_before+disease_before_binary_num
 + age_scaled + bmi_group, data=datalist[[1]])
m3$AIC

m4<-multinom(changesperiod_lastyr ~covid_status_minimal  *disease_before_binary_num+heavyperiod_before + contra_past12mo_groupall+ age_scaled + bmi_group , data=datalist[[1]])
m4$AIC # 



# Table
tab<-summary(pool_univariate[[1]])

tab$q.value <- p.adjust(tab$p.value,method = "BH")


tab2 <- tab %>% mutate(RRR = round (exp(estimate),2),
                      LowCI = round(exp (estimate - 1.96*std.error),2),
                      HighCI = round(exp (estimate + 1.96*std.error),2),
                      p.value = round ((p.value),4),
                      q.value = round ((q.value),4))%>%
                select(y.level ,term,RRR,LowCI,HighCI, p.value, q.value)

tab2

# export report
library(reporter)

tbl <- create_table(tab2) %>% 
  titles("Pooled Multivariate Models (Period Flow) ")
rpt <- create_report("Multi_fullFlow.pdf", font_size=  8, output_type = "PDF") %>% 
  add_content(tbl)
write_report(rpt)
```    
##### Print table
```{r print table_flow, results="asis"}
kable(tab2)
```


#### Plot
```{r plot_periodchanges, results="asis", fig.width=8}

## plot
levels(datalist[[1]]$changesperiod_lastyr)[4]<-"Lighter and Heavier"

m<-multinom(changesperiod_lastyr  ~  cycle_irreg_before_group+age_scaled +covid_status_minimal+ bmi_group +disease_before_binary_num  , data=datalist[[1]])


# Plot combined
#
# Save results
pprob_grplang <- ggeffect(m, terms = "covid_status_minimal")

# Build plot
plot_flow_figo_cov_comb<-ggplot(data = pprob_grplang,
       aes(x = x, y = predicted,
           color = response.level, group = response.level)) +
  #geom_line() +
  geom_point() +
  ggtitle("(C) Period flow")+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high,
                    color = response.level,
                    group = response.level),
                width = .1) +
  scale_color_brewer(palette = "Dark2",
                     name = "",
                     labels = c("Heavier",
                                "Lighter",
                                "Lighter & Heavier",
                                "No changes")) +
  labs(
    x = "",
    y = "Probability"
  ) +
  # Set the theme
#  theme_minimal(base_family="Avenir LT Std 35 Light")+
  theme_bw()+
  theme(
    legend.position = "bottom", # move legend to the bottom
    axis.title = element_text(size = 12) # increase axis title size
  )

ggsave("plot_flow_predicted.bmp",plot_flow_figo_cov_comb, width=5, height=5)

# print
plot_flow_figo_cov_comb


```


# Inter-menstrualbleeding


##### Model 

```{r IMB , echo=FALSE, include=FALSE}

# multinomial-------------------------------------------------------------------
p_load(nnet) # for multinomial model

# set global R options
pboptions(type = "timer", char = "=") # initialize progress bar

# set list of exposures to test
exposures <- c(
    Cs(
        covid_status_minimal  +cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num,
        covid_status_minimal  *cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num,
        covid_status_minimal  *contra_past12mo_groupall+cyclelength_before_group+disease_before_binary_num,
        covid_status_minimal  *disease_before_binary_num+cyclelength_before_group + contra_past12mo_groupall
    )
)



# model function - multivariate
 models <- function(x) {
     lapply(datalist, function(y)
         multinom(as.formula(
             paste0(
                 "changesspotting_lastyr ~ age_scaled + bmi_group + ",
                 x # exposure
            )
         ), data = y, model = TRUE)
     )
 }

## run  models
models_univariate <- as.list(seq(1,length(exposures))) # create list to store model results
models_univariate <- pblapply(exposures, models)





### Pool -------------------------------------------------------------------

pool_univariate <- as.list(seq(1,length(exposures))) # create list to store pool results

# run pool
for(j in seq_along(exposures)) {
    pool_univariate[[j]] <- pool(models_univariate[[j]])
}




### Get the table ------------------------------------------------------

### create report for model with age, bmi and contraceptive use
tab<-summary(pool_univariate[[1]])

tab$q.value <- p.adjust(tab$p.value,method = "BH")


tab2 <- tab %>% mutate(RRR = round (exp(estimate),2),
                      LowCI = round(exp (estimate - 1.96*std.error),2),
                      HighCI = round(exp (estimate + 1.96*std.error),2),
                      p.value = round ((p.value),4),
                      q.value = round ((q.value),4))%>%
                select(y.level ,term,RRR,LowCI,HighCI, p.value, q.value)



library(reporter)

tbl <- create_table(tab2) %>% 
  titles("Pooled Multivariate Models (Inter-Menstrual Bleeding) ")
rpt <- create_report("Multi_full_Spotting.pdf", font_size=  8, output_type = "PDF") %>% 
  add_content(tbl)
write_report(rpt)


##-----------------AIC models from 1st dataset
library(modelsummary)
library(kableExtra)
library(gt)
m<-multinom(changesspotting_lastyr ~ covid_status_minimal  +cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num+age_scaled + bmi_group , data=datalist[[1]])
m$AIC # 

m2<-multinom(changesspotting_lastyr ~         covid_status_minimal  *cyclelength_before_group+contra_past12mo_groupall+disease_before_binary_num + age_scaled + bmi_group , data=datalist[[1]])
m2$AIC #

m3<-multinom(changesspotting_lastyr ~         covid_status_minimal  *contra_past12mo_groupall+cyclelength_before_group+disease_before_binary_num + age_scaled + bmi_group, data=datalist[[1]])
m3$AIC #

m4<-multinom(changesspotting_lastyr ~ covid_status_minimal  *disease_before_binary_num+cyclelength_before_group + contra_past12mo_groupall+ age_scaled + bmi_group , data=datalist[[1]])
m4$AIC # 


```    


##### Print table
```{r print table_IMB , results="asis"}
kable(tab2)
```
##### Plot
```{r plot_IMB_normal, results="asis",  fig.width = 8}

#-------------------- plot predicted effect sizes

mod1<-multinom(changesspotting_lastyr ~ cyclelength_before_group +covid_status_minimal + age_scaled+ bmi_group +contra_past12mo_groupall+disease_before_binary_num, data=datalist[[1]])



# Save results
pprob_grplang <- ggeffect(mod1, terms = "covid_status_minimal")

# Build plot
plot_IMB_figo1_com<-ggplot(data = pprob_grplang,
       aes(x = x, y = predicted,
           color = response.level, group = response.level)) +
#  geom_line() +
  geom_point() +
  ggtitle("(D) Inter-menstrual bleeding")+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high,
                    color = response.level,
                    group = response.level),
                width = .1) +
  scale_color_brewer(palette = "Dark2",
                     name = "",
                     labels = c("Less",
                                "More",
                                "No changes",
                                "Less and more")) +
  labs(
    x = "",
    y = "Probability"
  ) +
  # Set the theme
#  theme_minimal(base_family="Avenir LT Std 35 Light")+
   theme_bw()+
    theme(
    legend.position = "bottom", # move legend to the bottom
    axis.title = element_text(size = 12) # increase axis title size
  )

ggsave("plot_IMB_predicted.bmp",plot_IMB_figo1_com, width=5, height=5)


# print
plot_IMB_figo1_com


```





# General Plot
```{r pplot_all, results="asis",  fig.width=8, fig.height=16}

## Plot covid predicted probabilities
library(ggpubr)


 
all<-grid.arrange(
  plot_freq_figo1_comb,
  plot_reg_figo1_comb,
  plot_flow_figo_cov_comb,
  plot_IMB_figo1_com,
  plot_dur_figo_covax_comb,
  plot_miss_figo_covax_comb,
  widths=c(5,5),
  heights=c(5,5,5))

# save
ggsave("plot_all_predicted.bmp",all, width=12, height=14)
ggsave("Figure5.pdf",all, width=12, height=14)

# print
all 


```


